\recipe[From the website thefoodiephysician.com]{Quinoa With Roasted Vegetables}
\serves{6}
\preptime{10 minutes}
\cooktime{35 minutes}
\contrib{Jake C}
\begin{ingreds}
    1 Medium Red Onion, thickly sliced
    2 Medium Zucchini, sliced
    2 Bell Peppers (yellow or red), sliced
    2 Carrots, peeled and sliced
    6-8 Whole Cloves of Garlic, peeled
    3 \(\frac{1}{2}\) Tablespoons of Olive Oil
    1 Tablespoon of Fresh Thyme (or 1 teaspoon dried)
    1 Cup of Quinoa
    2 Cups of Vegetable Stock
    1 Tablespoon of Balsamic Vinegar
    \(\frac{1}{2}\) Teaspoon of Dijon Mustard
    Kosher salt
    Black pepper
\end{ingreds}
\vspace{.5in}
\begin{method}[Preheat the oven to \temp{425}]
     Place the onion, zucchini, bell peppers, carrots, and garlic on a large roasting pan. Drizzle with 1½ tablespoons of olive oil. Sprinkle the thyme on top and season with a pinch of salt and pepper.
     
Roast in the oven until vegetables are softened and caramelized, 30-35 minutes. If using two baking sheets, rotate the pans halfway through.
    
    While vegetables are roasting, make the quinoa. Place the quinoa and vegetable (or chicken) stock in a medium saucepan and bring to a boil over high heat. Cover the pot and reduce heat to low. Simmer until cooked, 12-15 minutes. Season with salt to taste. Remove from heat and transfer quinoa to a large bowl. Add the roasted vegetables to the bowl.
    
    Whisk the remaining 2 tablespoons olive oil with the balsamic vinegar and Dijon mustard in a small bowl. Pour the dressing over the quinoa and vegetables and toss to combine. Serve warm or cold.
\end{method}